IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-10-26 ms.tex
Relabled arcsec.
I found out the duration of the observations.

\begin{table*}
\begin{center}
\begin{tabular}{cccc}
Name & Rotation Period & Spectral Type & K magnitude \\
-- & hr & -- & -- \\
2MASS J1821+14010 & 4.2 & L5 & 11.14 \\
2MASS J0835-019 & 9 & L5 & 11.65 \\
\end{tabular}
\end{center}
\end{table*}

\section{Observations}
We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24 \arcsec.
We were able to measure spectrophotometry over ? hours, which was greater than one full rotation period of the brown dwarf.
Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px

@@

\section{Light Curves}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
\caption{Sine fit amplitude versus wavelength for 2MASS J1821. The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
\end{figure}

>>>>

\begin{table*}
\begin{center}
\begin{tabular}{cccc}
Name & Rotation Period & Spectral Type & K magnitude \\
-- & hr & -- & -- \\
\hline \hline
2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L5 & 11.14 \\
2MASS J0835-019 & 9 & L5 & 11.65 \\
\end{tabular}
\end{center}
\end{table*}

\section{Observations}
We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24\arcsec.
We were able to measure spectrophotometry over 7.47 hours, which was 1.78 rotations at the rotation period.
Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
\caption{Sine fit amplitude versus wavelength for 2MASS J1821. The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
\end{figure}
